% 
% Information Retrieval
% -------------------------------
% University of California Irvine
% 
% Author:
% - María Carrasco Rodríguez
% - Fabs Lindenberg
% - Lea Vael

\documentclass[a4paper,11pt,oneside]{book}
\usepackage{wrapfig} 
\usepackage{helvet}
\usepackage{phdthesis}
\usepackage{kostspielig}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{appendix}
\usepackage{pifont}
\usepackage{color}
\usepackage{amsmath}
\usepackage{epsfig}


%\pagestyle{fancy}
%\fancyhead{}
%\fancyhead[L]{\textsf{\textbf{CS 221 Information Retrieval}\\ Assignment 2}}
%\fancyhead[R]{\textsf{Maria Carrasco (16874129)\\ Fabian Lindenberg (74076658)}}
%\fancyfoot[R]{\textsf{\thepage}}
%\renewcommand{\footrulewidth}{0.4pt}
%\cfoot[]{}


\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}

\hypersetup{colorlinks, 
           linkbordercolor= 1 0.8 0.8,
           citecolor=black,
           filecolor=black,
           linkcolor=black,
           urlcolor=black,
           bookmarksopen=true,
           pdftex}
\title{Information Retrieval }
\subtitle{Assignment 4}
\location{University of California Irvine}
\author{ María Carrasco Rodríguez (16874129) \\
		Fabian Lindenberg (74076658)\\
		Lea Vael ()}



\begin{document}

\kostspieligmaketitle

%\tableofcontents
%\pagebreak
% \startapendix

\chapter{Context}
\section{Summary}
Enron grew from nowhere to be America's seventh largest company in just 15 years. The energy company company employed 21,000 staff in more than 40 countries and had affiliations that included The White House. But the firm's success turned out to have involved an elaborate scam. 

The collapse of Enron was revealed in october 2001. {\it Enron Corporation} went bankrupt as a result of committing institutionalized, systematic and well-planned accounting fraud. This also leaded to the dissolution of one of the largest accounting firms, {\it Arthur Andersen}. Not only has it been the largest bankruptcy reorganization in American history, but also the biggest audit failure.


\section{Timeline of the main events}
\url{http://www.chron.com/news/specials/enron/timeline.html}

\section{Year of the main events}
Major events were developed in {\bf2001}.
\section{Players}
\begin{description}
\item[Kenneth Lay] \ding{32}
\begin{itemize}
\item Former CEO of Enron, helped start the company. 
\item Enron extended to him \$7.5 million revolving credit line, which he reportedly used and repaid with Enron stock 15 times within a period of just several months
\item He quit as CEO in February 2001
\item He returned as CEO in August 2001until he resigned on Jan. 23, 2002 
\item He quit the Enron board altogether on Feb. 4. 
\item Sherron Watkins said Lay was "duped" by top executives
\end{itemize}
\item[Jeffrey Skilling]  \ding{32}
\begin{itemize}
\item Enron's chief executive in the first half of 2001
\item Since joining the company in 1990, Skilling helped transform Enron from a natural-gas pipeline company into an energy-trading powerhouse.
\item Between January and August 2001 he sold off about \$20 million in Enron stock
\item Resigned after the close of markets on Aug. 14 2001
\item Being charged with conspiracy, fraud and insider trading
\end{itemize}
\item [David Duncan]  \ding{32}
\begin{itemize}
\item Enron's chief auditor at Anderson
\item His job was to check Enron’s accounts
\item He is accused of ordering the shredding of thousands of Enron-related documents in an effort to hide them from Securities and Exchange Commission investigators
\end{itemize}

\item[Andrew Fastow]  \ding{32}
\begin{itemize}
\item Former Chief Financial Officer of Enron
\item The mastermind behind the deceptive accounting practices
\item Lea Fastow (his wife) also plead guilty to signing and filing a tax return that did not include income the Fastow’s had received from Mike Kopper 
\end{itemize}

\item [Sherron Watkins]  \ding{32}
\begin{itemize}
\item Known as the "Enron whistle-blower" 
\item Was Enron's vice president of corporate development
\item Wrote a letter to Kenneth Lay about “suspicions of accounting improprieties"  
\item Not really a “whistle-blower” because she never went public with her suspicions

\end{itemize}
\end{description}

\pagebreak
\begin{thebibliography}{XXX}
	\bibitem{1} \url{http://en.wikipedia.org/wiki/Enron_scandal}
	\bibitem{2} \url{http://en.wikipedia.org/wiki/Enron}
	\bibitem{3} \url{http://news.bbc.co.uk/2/hi/business/1780075.stm}
	\bibitem{3} \url{http://www.stat.unc.edu/faculty/cji/fys/2004/Enron.ppt}
	\bibitem{3} \url{http://whatreallyhappened.com/WRHARTICLES/enron.html}
	\bibitem{3} \url{http://fpc.state.gov/documents/organization/8038.pdf}
\end{thebibliography}



\end{document}
