% 
% Information Retrieval
% -------------------------------
% University of California Irvine
% 
% Author:
% - María Carrasco Rodríguez
% - Fabs Lindenberg
% - Lea Voget

\documentclass[a4paper,11pt,oneside]{book}
\usepackage{wrapfig} 
\usepackage{helvet}
\usepackage{phdthesis}
\usepackage{kostspielig}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{appendix}
\usepackage{pifont}
\usepackage{color}
\usepackage{amsmath}
\usepackage{epsfig}


%\pagestyle{fancy}
%\fancyhead{}
%\fancyhead[L]{\textsf{\textbf{CS 221 Information Retrieval}\\ Assignment 2}}
%\fancyhead[R]{\textsf{Maria Carrasco (16874129)\\ Fabian Lindenberg (74076658)}}
%\fancyfoot[R]{\textsf{\thepage}}
%\renewcommand{\footrulewidth}{0.4pt}
%\cfoot[]{}


\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO: #1}}}

\hypersetup{colorlinks, 
           linkbordercolor= 1 0.8 0.8,
           citecolor=black,
           filecolor=black,
           linkcolor=black,
           urlcolor=black,
           bookmarksopen=true,
           pdftex}
\title{Information Retrieval }
\subtitle{Assignment 5}
\location{University of California Irvine}
\author{ María Carrasco Rodríguez (16874129) \\
		Fabian Lindenberg (74076658)\\
		Lea Voget (45869178)}



\begin{document}

\kostspieligmaketitle

%\tableofcontents
%\pagebreak
% \startapendix

\chapter{Context}
\begin{description} \vskip 1cm
\item [\underline{{\it Pride and Prejudice} by Jane Austen}]  \ding{32}
	\begin{itemize}
	\item [{\bf year}] The novel was written between October of 1796 and August of 1797.
	\item [{\bf summary}] Jane Austen’s classic novel chronicles the events in the lives of the Bennet family. Take a family with five unmarried daughters and a lack of wealth, throw in a new wealthy neighbor or two, plus a whole regiment of soldiers in town, and add a heaping spoonful of pride and a pinch of prejudice. Mix it all together and you get a story full of tears and laughter, embarrassment and pride, and, of course, love.
	\item [{\bf URL}] \url{http://www.enotes.com/pride-and-prejudice}
	\end{itemize} 
\item [\underline{{\it Emma} by Jane Austen}]  \ding{32}
	\begin{itemize}
	\item [{\bf year}] Austen wrote {\it Emma} between January of 1814 and March of 1815.
	\item [{\bf summary}] Sherry reads Jane Austen’s sparkling comedy of manners with wit and vivacity, and brings the characters to life. Mr. Woodhouse worries and frets, Miss Bates chatters on, and Emma blithely manipulates and misunderstands her friends and family until she finally learns her lesson! 
	\item [{\bf URL}] \url{http://www.online-literature.com/austen/emma/}
	\end{itemize} 
\item [\underline{{\it Jane Eyre} by Charlotte Bronte}] \ding{32}
	\begin{itemize}
	\item [{\bf year}] 1847
	\item [{\bf summary}] Jane Eyre is not your typical romance. It is a story of a woman who struggles with a world in which she doesn’t quite fit. Once finished with her schooling, and with no family that really cares for her she strikes out on her own as a governess. Jane Eyre searches for love, someone to care for her, and someone to care for, and finds it in unexpected places.
	\item [{\bf URL}] \url{http://jco.usfca.edu/text/eyre.html}
	\end{itemize} 
\item [\underline{{\it Moby Dick} by Herman Melville}]  \ding{32}
	\begin{itemize}
	\item [{\bf year}] 1851
	\item [{\bf summary}] Moby-Dick recounts the adventures of the narrator Ishmael as he sails on the whaling ship Pequod under the command of Captain Ahab. Ishmael believes he has signed onto a routine commission aboard a normal whaling vessel, but he soon learns that Captain Ahab is not guiding the Pequod in the simple pursuit of commerce but is seeking one specific whale, Moby-Dick, a great while whale infamous for his giant proportions and his ability to destroy the whalers that seek him. Captain Ahab is bent on revenge because of his leg and he intends to get Moby-Dick. The encounter with Moby-Dick brings a tragic end to the affair. Ishmael alone survives, using his friend Queequeg's coffin as a flotation device until he is ironically rescued by the Rachel, which has continued to search for its missing crew.
	\item [{\bf URL}] \url{http://www.americanliterature.com/Melville/MobyDickorTheWhale/MobyDickorTheWhale.html}
	\end{itemize} 
\item [\underline{{\it Anna Karenina} by Leo Tolstoy}] \ding{32}
	\begin{itemize}
	\item [{\bf year}] 1875
	\item [{\bf summary}] The narrative centers on the adulterous affair between Anna, wife of Aleksey Karenin, and Count Vronsky, a young bachelor. Karenin's discovery of the liaison arouses only his concern for his own public image. Anna promises discretion for the sake of her husband and young son but eventually becomes pregnant by Vronsky. After the child is born, Anna and the child accompany Vronsky first to Italy, then to his Russian estate. She begins making furtive trips to see her older child and grows increasingly bitter toward Vronsky, eventually regarding him as unfaithful. In desperation she goes to the train station, purchases a ticket, and then impulsively throws herself in front of the incoming train. A parallel love story, involving the difficult courtship and fulfilling marriage of Kitty and Levin, provides rich counterpoint to the tragedy and is thought to reflect Tolstoy's own marital experience.  Anna pays not so much because she transgresses the moral code but because she refuses to observe the proprieties customarily exacted in such liaisons by the hypocritical high society to which she belongs.
	\item [{\bf URL}] \url{http://us.penguingroup.com/static/rguides/us/anna_karenina.html}
	\end{itemize}
\item [\underline{{\it Three Men in a Boat} Jerome K. Jerome}] \ding{32}
	\begin{itemize}
	\item [{\bf year}] 1889
	\item [{\bf summary}] The book centers around 3 men who go on a boat trip with a dog, and various anecdotes regarding travel and life. The three men are George, Harris and the narrator, who are all massive hypochiandriacs -- they find that they have symptoms of every disease in existance (except housemaid's knee). To prop up their failing health, they decide to take a cruise down the Thames in a rented boat, camping and enjoying nature's bounty. Along with Monty -- an angelic-looking, devilish terrier -- the three friends set off down the river. But they find that not everything is as easy as they expected. They get lost in hedge mazes, end up going downstream without a paddle, encounter monstrous cats and vicious swans, have picnics navigate locks, offend German professors, and generally get into every kind of trouble they possibly can...

	\item [{\bf URL}] \url{http://www.jeromekjerome.com/About_Jerome/three_men}
	\end{itemize}
\item [\underline{{\it The Portrait of a Lady} by Henry James}] \ding{32}
	\begin{itemize}
	\item [{\bf year}] 1875
	\item [{\bf summary}] It is the story of a spirited young American woman, Isabel Archer, who “affronts her destiny” and finds it overwhelming. She inherits a large amount of money and subsequently becomes the victim of Machiavellian scheming by two American expatriates. 
	\item [{\bf URL}] \url{http://www.shmoop.com/portrait-of-a-lady/}
	\end{itemize}
\end{description}


\pagebreak
\begin{thebibliography}{XXX}
	\bibitem{1} \url{www.austen.com/}
	\bibitem{2} \url{http://librivox.org/}
	\bibitem{3} \url{http://en.wikipedia.org/}
	\bibitem{4} \url{http://www.online-literature.com}
	\bibitem{5} \url{http://www.goodreads.com/}
	\bibitem{6} \url{http://www.sparknotes.com/}
	\bibitem{7} \url{http://www.flintfordreams.com/2010/11/22/three-men-in-a-boat-by-jerome-k-jerome/}
	\bibitem{8} \url{http://bogormen.livejournal.com/32248.html}
\end{thebibliography}



\end{document}
